---
title: "ESM 204 Assignment 4"
author: "Jill Wirt & Eleonore Durand"
date: "6/3/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
sector_data <- read_csv("HW4Data.csv")

```

```{r #1}
aregress <- lm(MC_A ~ Abatement, data= sector_data)
sectorapff=function(x){aregress$coefficients[2]*x +aregress$coefficients[1]}

bregress <-lm(MC_B ~ Abatement, data= sector_data)
sectorbpff=function(x){bregress$coefficients[2]*x +bregress$coefficients[1]}

cregress <-lm(MC_C ~ Abatement, data= sector_data)
sectorcpff=function(x){cregress$coefficients[2]*x +cregress$coefficients[1]}

dregress <-lm(MC_D ~ Abatement, data= sector_data)
sectordpff=function(x){dregress$coefficients[2]*x +dregress$coefficients[1]}


newdata<- sector_data %>% 
  mutate(A2=(Abatement)*(Abatement))

aquad <- lm(MC_A ~ Abatement + A2, data= newdata)
quada=function(x){aquad$coefficients[2]*x +aquad$coefficients[3]*x^2+ aquad$coefficients[1]}

bquad <-lm(MC_B ~ Abatement + A2, data= newdata)
quadb=function(x){bquad$coefficients[2]*x +bquad$coefficients[3]*x^2+ bquad$coefficients[1]}

cquad <-lm(MC_C ~ Abatement + A2, data= newdata)
quadc=function(x){cquad$coefficients[2]*x +cquad$coefficients[3]*x^2+ cquad$coefficients[1]}

dquad <-lm(MC_D ~ Abatement + A2, data= newdata)
quadd=function(x){dquad$coefficients[2]*x +dquad$coefficients[3]*x^2+ dquad$coefficients[1]}


#c and d have better fit with a quad function

predicteda <-newdata %>% 
   mutate(linear= predict(aregress, newdata= newdata, type="response")) %>% 
  mutate(quad= predict(aquad, newdata= newdata, type="response")) %>% 
  select(Abatement, MC_A, linear, quad, A2)

plota <- ggplot(predicteda, aes(x=Abatement, y=MC_A)) +
  geom_point()+
  geom_smooth(method= lm)+
  theme_classic() 

# plota 
```

```{r #1 assign coefficients}

# Assign regression slope and intercepts to variables

### A
A_abatement <- aregress$coefficients[2]
A_intercept <- aregress$coefficients[1]

### B
B_abatement <- bregress$coefficients[2]
B_intercept <- bregress$coefficients[1]

### C
C_abatement <- cregress$coefficients[2]
C_intercept <- cregress$coefficients[1]

### D
D_abatement <- dregress$coefficients[2]
D_intercept <- dregress$coefficients[1]

```



2. Using these models and the current level of carbon emissions, derive each sector’s demand curve for carbon emissions. In other words, how much would each sector be willing to pay for the right to pollute the first unit, second unit, etc? Draw these demand curves on a graph. Which sector is willing to pay the most for the first unit of carbon emissions?

```{r #2}

# JUST USED LINEAR REGRESSIONS COEFFICIENTS FOR ALL CALCULATIONS

# #### SECTOR A WILLINGNESS TO PAY
# Current emissions are 180 - use quantities from 0 to 180 by 10

quantity_a <- seq(0,180,by=10)
# Write function for demand curve for Sector A
demand_A <- function(q){
  (A_abatement*(180-q)) + A_intercept
}

demand_A


# Derive demand curve using the values above
d_curve_A <- demand_A(quantity_a)



# Graph the demand curve
curve(demand_A, from=0, to=180, xlab = "Carbon Emissions (tons)", ylab = "$/Ton")


### Plug in 0 to the function to calculate how much Sector A is willing to pay to emit the first unit of Carbon

WTP_A <- (A_abatement*(180-0) + A_intercept)

# Sector A is willing to pay 95.20 for the first ton of emissions 

####################################
# #### SECTOR B WILLINGNESS TO PAY

# Current emissions are 200 - use quantities from 0 to 200 by 10
quantity_b <- seq(0,200,by=10)
# Write function for demand curve for Sector B
demand_B <- function(q){
  (B_abatement*(200-q)) + B_intercept
}

demand_B

# Derive demand curve using values above
d_curve_B <- demand_B(quantity_b)

# Graph the demand curve
curve(demand_B, from=0, to=200, xlab = "Carbon Emissions (tons)", ylab = "$/Ton")

# Plug in 0 to the function to calculate how much Sector B is willing to pay to emit the first unit of Carbon

WTP_B <- (B_abatement*(200-0) + B_intercept)
# Sector B is willing to pay $49.07 for the first ton of emissions

####################################
### Sector C WTP

quantity_c <- seq(0,220,by=10)
# Write function for demand curve for Sector B
demand_C <- function(q){
  (C_abatement*(220-q)) + C_intercept
}

demand_C

# Derive demand curve using values above
d_curve_C <- demand_C(quantity_c)

# Graph the demand curve
curve(demand_C, from=0, to=220, xlab = "Carbon Emissions (tons)", ylab = "$/Ton")

# Plug in 0 to the function to calculate how much Sector C is willing to pay to emit the first unit of Carbon

WTP_C <- (C_abatement*(220-0) + C_intercept)
# Sector C is willing to pay $160.79 for the first ton of emissions

####################################
### Sector D WTP

quantity_d <- seq(0,300,by=10)
# Write function for demand curve for Sector B
demand_D <- function(q){
  (D_abatement*(300-q)) + D_intercept
}

demand_D

# Derive demand curve using values above
d_curve_D <- demand_D(quantity_d)

# Graph the demand curve
curve(demand_D, from=0, to=300, xlab = "Carbon Emissions (tons)", ylab = "$/Ton")

# Plug in 0 to the function to calculate how much Sector D is willing to pay to emit the first unit of Carbon

WTP_D <- (D_abatement*(300-0) + D_intercept)
# Sector D is willing to pay $87.66 for the first ton of emissions

### Sector C is willing to pay the most for the first ton of emissions.
```



3. Now focus on country X (which contains sectors A, B, and C). Assume there are no “co-benefits” from carbon abatement (i.e. that there are no local pollutants that are affected by carbon abatement). Suppose to meet the Paris Accord commitments, country X needs to cut all carbon emissions in half. For each of the policy options listed below, derive: (1) the total cost of meeting the target in country X, (2) the cost (or benefit) to each sector, and (3) the tax revenue generated.

```{r #3a}
# 3a) Cap on Carbon: Each sector (A, B, C) must cut is carbon emissions by 100 tons (thus reducing total emissions from 600 down to 300). 
#integrate marginal abatement curve for each sector from 0-100 

acostcap<- integrate(sectorapff, 0, 100)
#2019.762

bcostcap<- integrate(sectorbpff, 0, 100)
#1925.491 

ccostcap<- integrate(sectorcpff, 0, 100)
#2743.63

totalcostcap <- acostcap$value + bcostcap$value + ccostcap$value

#find total cost under new policy: A would go to 80, B would go to 100, C would go to 120



```

```{r #3b}
# 3b) Tax on Carbon: To emit a ton of carbon in country X, you must pay a tax of $t. You will need to find the tax that accomplishes the desired reduction. 


#aggregate marginal abatement cost 
dividedby<- (1/A_abatement+1/B_abatement+1/C_abatement)/3
intercept<- ((aregress$coefficients[1]/-aregress$coefficients[2])-B_intercept/B_abatement +C_intercept/-C_abatement)/3
aggmca <- function(x){(x+(-intercept))/dividedby}




```

```{r #3c}
# 3c) Cap and trade: Each sector (A, B, C) is allocated carbon permits equal to their current emissions minus 100 (same as in (a) above), thus achieving the total reduction of 300. Then these three sectors are allowed to trade with each other. You will need to derive the outcome of that trading.





```



4. Again, without any co-benefits, suppose that country Y (which only has one carbon-emitting sector, D) has no obligation to reduce its emissions. Country X asks country Y to enter the country X carbon market. Doing so would require country Y to put a cap on carbon emissions at its current level of emissions (300 tons), but would then allow country Y to sell carbon offsets to sectors A, B, or C. Are there any incentives for country Y to enter country X’s carbon market and to thus place a voluntary cap on its emissions? Are there any incentives for country X to try to attract country Y into its market?

```{r #4}









```



5. Now assume that every ton of carbon emissions creates 1 ton of local air pollution. Local air pollution causes economic damages (health, environmental, etc.), but only in the country in which it is emitted. Assume there are no local air pollution regulations in either country X or country Y.
```{r #5a}
# 5a) In a carbon cap and trade market that only covers sectors in country X, how much local air pollution would you expect in Country X? Country Y?





```

```{r #5b}
# 5b) If country Y enters the carbon market for country X (as in question 4 above), how much local pollution will there be in country X and Country Y?






```

```{r #5c}
# 5c) What advice can you give country X and country Y about the desirability of allowing international trade of carbon emissions credits?








```